Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

	\item Well known issues in Brownbridge garbage collectors are fixed and complete and safe garbage collector is designed after three successive failures.
	\item Theoretically, our shared memory garbage collector detects garbage traverses affected the graph of objects 7 traversals less than the state of the art concurrent reference counted garbage collector.
	\item This thesis presents first known locality based concurrent multi-collector scalable garbage collector with no global synchronization in the distributed memory system. The garbage collector contains complete proof of the system.
	\item Distributed garbage collector introduces a novel weight based approach to convert the graph into directed acyclic graph and thereby detecting cycles faster.
	\item Garbage collector that finishes in linear time in a number of edges in the affected subgraph, a part of an original subgraph is better than tracing entire heap in the distributed memory systems.

>>>>

	\item Well known issues in Brownbridge garbage collectors are fixed and complete and a safe garbage collector is designed.
	\item Theoretically, our shared memory garbage collector detects garbage  in fewer traversals than other state of the art concurrent reference counted garbage collector.
	\item This thesis presents the first known locality-based concurrent multi-collector scalable distributed garbage collector with no global synchronization. The thesis contains a complete proof of the garbage collector.
	\item The distributed garbage collector introduces a novel weight based approach to convert the graph into a directed acyclic graph and thereby detects cycles faster.
	\item The designed garbage collector algorithms finishes garbage collection in linear time.
